---
title: "Untitled"
author: "Ariel Marcy"
date: "12/3/2020"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/Documents/Work/Science/Research/2020 UNL DBER/Co-Teaching")
```

## Read in data and packages
```{r}
library(stringr)

raw <- read.csv("SurveyDataDI.csv", header = TRUE)
```

## Fix Academic Rank to ascend with rank
```{r}
t.data <- raw
t.data$AcadRank <- t.data$AcadRank * 10  # mark old numbers

# Sub in new ones
t.data$AcadRank[which(t.data$AcadRank == 10)] <- 6  # Prof
t.data$AcadRank[which(t.data$AcadRank == 20)] <- 5  # A/Prof
t.data$AcadRank[which(t.data$AcadRank == 30)] <- 4  # Asst P
t.data$AcadRank[which(t.data$AcadRank == 40)] <- 3  # lecturer
t.data$AcadRank[which(t.data$AcadRank == 50)] <- 2  # visiting
t.data$AcadRank[which(t.data$AcadRank == 60)] <- 1  # pre-prof
t.data$AcadRank[which(t.data$AcadRank == 70)] <- 1  # pre-prof

rank.names <- c("PreProf", "Visit.", "Lecture", "Asst. P", "A/Prof", "Prof")

t.data$CoordPattern <- as.character(raw$CoordPattern) 
```

## Redefine "Coordination Pattern" into 3x4 table of broader categories
```{r}
u.coords <- unique(t.data$CoordPattern) 

# Subset to just chemistry
tc.data <- t.data[which(t.data$Discipline == 3), ]

# Subset the datasets
text.1 <- tc.data[str_which(tc.data$CoordPattern, "1[123][123][123]"), ]  # solo
text.2 <- tc.data[str_which(tc.data$CoordPattern, "2[123][123][123]"), ]  # coll
text.3 <- tc.data[str_which(tc.data$CoordPattern, "3[123][123][123]"), ]  # cont

exam.1 <- tc.data[str_which(tc.data$CoordPattern, "[123]1[123][123]"), ]  # solo
exam.2 <- tc.data[str_which(tc.data$CoordPattern, "[123]2[123][123]"), ]  # coll
exam.3 <- tc.data[str_which(tc.data$CoordPattern, "[123]3[123][123]"), ]  # cont

cont.1 <- tc.data[str_which(tc.data$CoordPattern, "[123][123]1[123]"), ]  # solo
cont.2 <- tc.data[str_which(tc.data$CoordPattern, "[123][123]2[123]"), ]  # coll
cont.3 <- tc.data[str_which(tc.data$CoordPattern, "[123][123]3[123]"), ]  # cont

inst.1 <- tc.data[str_which(tc.data$CoordPattern, "[123][123][123]1"), ]  # solo
inst.2 <- tc.data[str_which(tc.data$CoordPattern, "[123][123][123]2"), ]  # coll
inst.3 <- tc.data[str_which(tc.data$CoordPattern, "[123][123][123]3"), ]  # cont
```

## Function to get important values by dataset
```{r}
MakeTECItable <- function(dataset) {
        # Get total n
        dataset <- dataset[complete.cases(dataset$RBISuse), ]
        N <- dim(dataset)[1]
        
        # Get percent RBIS
        perRBIS <- signif(((length(which(dataset$RBISuse == 2)) / N ) *100), 3)
        
        # Get the top three coordination patterns
        pat.freq <- table(dataset$CoordPattern)
        top.3 <- dimnames(pat.freq[order(pat.freq, decreasing = T)])[[1]][1:3]
        top.3.n <- pat.freq[order(pat.freq, decreasing = TRUE)[1:3]]
        top.3.eng <- paste("Top 3: ", top.3[1], " (n=", top.3.n[1], "), ", top.3[2], " (n=", top.3.n[2], "), ", top.3[3], " (n=", top.3.n[3], ")", sep = "")
        TECIbox <- list(N, perRBIS, top.3.eng)
        return(TECIbox)        
        
}



MakeTECItable(inst.3)
MakeTECItable(inst.2)
MakeTECItable(inst.1)
```

## Split by discipline
```{r}
# Create subdiscipline datasets and remove rows with NAs
chem.dat <- t.data[which(t.data$Discipline == 1), ]
chem.dat <- chem.dat[complete.cases(chem.dat), ]
table(chem.dat$AcadRank)

math.dat <- t.data[which(t.data$Discipline == 2), ]
math.dat <- math.dat[complete.cases(math.dat), ]
table(math.dat$AcadRank)

phys.dat <- t.data[which(t.data$Discipline == 3), ]
phys.dat <- phys.dat[complete.cases(phys.dat), ]
table(phys.dat$AcadRank)
```


## Get relative frequencies by y-categories
Use nested for loops to replace each cell with the appropriate relative frequency given by: (number of instructors of rank i using k teaching style) / (number of instructors in rank i) * 100

Academic Rank - TEST
```{r}
rank_counts <- table(chem.dat$AcadRank)  # n respondants per X-axis category (Academic Rank)
rank_freq <- as.matrix(table(chem.dat$Coord_Cat, chem.dat$AcadRank))  # frequencies of rank (x axis columns) by teaching style (y-axis rows)


rank_counts <- table(math.dat$AcadRank)  # n respondants per X-axis category (Academic Rank)
rank_freq <- as.matrix(table(math.dat$Coord_Cat, math.dat$AcadRank))  # frequencies of rank (x axis columns) by teaching style (y-axis rows)




# Order frequency table by PC1 score
rank_freq <- rank_freq[, match(Teach_by_PC1, as.numeric(unlist(dimnames(rank_freq)[2][1])))]  # reorder columns (teaching seq) by PC1 score

# Make relative frequency table
rank_rf <- rank_freq  # initialize relative freq table
for(i in 1:dim(rank_rf)[1]) {  # for loops to convert frequencies into %s
        for (k in 1:dim(rank_rf)[2]) {
                rank_rf[i, k] <- signif(rank_rf[i, k] / rank_counts[i], 2) * 100  # relative frequency as a % with 2 significant digits
        }
}
```

## Plot & export results - RANK
```{r}
pdf("../Rank_PC1_plot.pdf")

plot(rep(1:dim(rank_rf)[2], dim(rank_rf)[1]),  # x-values go L-->R, Low-->High
     c(rep(1, 54), rep(2, 54), rep(3, 54), rep(4, 54), rep(5, 54), rep(6, 54), rep(7, 54)),                            # y-values match the order given above
     pch = 16,
     axes = FALSE,
     main = "Frequency of teaching types by academic rank",
     xlab = "more solitary <------- more coordinated -------> more controlled",
     ylab = "Rank",
     cex = (as.vector(t(rank_rf)) / 10), # rel. freq point sizes match above
     col = rgb(red = 0, green = 0, blue = 1, alpha = 0.6))  # alpha sets transparency

# Label x-axis by teaching sequence in order of PC1 score
axis(side = 1, at = c(1:54), labels = PC1_order$CoordPattern, las = 2, cex.axis = 0.5)

# Label y-axis with human-readable labels
y_labels = c("Prof", "A/Prof", "Asst/P", "Lect.", "Visit.", "Postdoc", "Grad")
axis(side = 2, at = c(1:7), labels = y_labels, las = 1, cex.axis = 0.75)

# Legend
freq_labels <- c("1%", "5%", "10%", "25%", paste(max(rank_rf), "%", sep = ""))
freq_pch <- c(1, 5, 10, 25, max(rank_rf))
legend("bottomright", freq_labels, col = rgb(0, 0, 1, alpha = 0.6), pch = 16, pt.cex = freq_pch / 10, text.width = 4, text.col = "darkgray", xjust = 1)

dev.off()  # completes export
```


## Get relative frequencies by y-categories - Discipline
```{r}
dis_counts <- table(raw$Discipline)  # n respondents per dicipline 
dis_freq <- table(raw$Discipline, raw$CoordPattern)  # freqs by discipline

# Order frequency table by PC1 score
dis_freq <- dis_freq[, match(Teach_by_PC1, as.numeric(unlist(dimnames(dis_freq)[2][1])))]  # reorder columns (teaching seq) by PC1 score

# Relative Frequencies
dis_rf <- dis_freq  # initialize relative frequency table
for(i in 1:dim(dis_freq)[1]) {  # for loops to convert frequencies into %s
        for (k in 1:dim(dis_freq)[2]) {
                dis_rf[i, k] <- signif(dis_rf[i, k] / dis_counts[i], 2) * 100  # relative frequency as a % with 2 significant digits
        }
}
```

## Plot and export
Discipline
```{r}
pdf("../Discipline_PC1_plot.pdf")  # set up for export

plot(rep(1:dim(dis_rf)[2], dim(dis_rf)[1]),  # x-values from L-->R, Low-->High
     c(rep(1, 54), rep(2, 54), rep(3, 54)),  # y-values match the above
     pch = 16,
     axes = FALSE,
     main = "Frequency of teaching types relative to discipline",
     xlab = "more solitary <------- more coordinated -------> more controlled",
     ylab = "Discipline",
     cex = (as.vector(t(dis_rf)) / 10),  # rel. freq point sizes match above
     col = rgb(red = 0, green = 0, blue = 1, alpha = 0.6))  # alpha sets transparency)

# Label x-axis by teaching sequence in order of PC1 score
axis(side = 1, at = c(1:54), labels = PC1_order$CoordPattern, las = 2, cex.axis = 0.5)

# Label y-axis with human-readable labels
y_labels = c("Chemistry", "Math", "Physics")
axis(side = 2, at = c(1:3), labels = y_labels, las = 1, cex.axis = 0.75)

# Legend
freq_labels <- c("1%", "5%", "10%", "25%", paste(max(dis_rf), "%", sep = ""))
freq_pch <- c(1, 5, 10, 25, max(dis_rf))
legend("bottomright", freq_labels, col = rgb(0, 0, 1, alpha = 0.6), pch = 16, pt.cex = freq_pch / 10, text.width = 4, text.col = "darkgray", xjust = 1)

dev.off()  # finish export
```
